Evidence of widspread maintenence of functional composition in vertebrate communities

### 2021-09-07 paper/manuscript.Rmd
more citations

While functional loss is frequently cited as one of the most pressing concerns of the anthropocene [@cardinale2012; @dirzo2014; @young2016], it is not necessarily inevitable even in scenarios of species loss [@daz2001].
Forecasts of functional loss range from negligible [@gallagher2013] to dire [@petchey2002; @pimiento2020].
And while some observed trends show significant functional loss [@flynn2009] others document no loss even in some of the most heavily impacted communities [@edwards2013; @matuoka2020].
On paleoecological time scales, functional composition is often conserved alongside species diversity even in the face of drastic environmental change [@jackson2015; @barnosky2005].
It is therefore critical to establish whether or not functional loss is the general rule for communities on time scales relevant for current environmental impacts.

@@

This study represents the best available data and biodiversity synthesis approaches.
Why then do we find no change in functional diversity despite extensive predictions to the contrary from both **theory** <!-- need more theory in the intro? --> and and many local studies?
First, the Biotime database is not a representative sample of the world's biodiversity or areas of greatest threat [@gonzalez2016; @vellend2017] (other sampling citation!), and the subset of data in this study exhibits a strong Northern Hemisphere bias.
We may simply not have data from those areas experiencing the greatest functional shifts [hughes2021].
We do however emphasize that even disturbed communities maintain functional structure [@edwards2013; @matuoka2020], and the inclusion of more heavily impacted sites would not necessarily change the result.

>>>>

While functional loss is frequently cited as one of the most pressing concerns of the anthropocene [@cardinale2012; @dirzo2014; @young2016], it is not necessarily inevitable even in scenarios of species loss [@daz2001]. Forecasts of functional loss range from negligible [@gallagher2013] to dire [@petchey2002; @pimiento2020]. And while some observed trends show significant functional loss [@flynn2009] others document no loss even in some of the most heavily impacted communities [@edwards2013; @matuoka2020]. On paleoecological time scales, functional composition is often conserved alongside species diversity even in the face of drastic environmental change [@jackson2015; @barnosky2004].
It is therefore critical to establish whether or not functional loss is the general rule for communities on time scales relevant for current environmental impacts.

@@

This study represents the best available data and biodiversity synthesis approaches.
Why then do we find no change in functional diversity despite extensive predictions to the contrary from both **theory** <!-- need more theory in the intro? --> and and many local studies?

First, the Biotime database is not a representative sample of the world's biodiversity or areas of greatest threat [@gonzalez2016; @vellend2017], and the subset of data in this study exhibits a strong Northern Hemisphere bias. We may simply not have data from those areas experiencing the greatest functional shifts [@hughes2021]. We do however emphasize that even disturbed communities maintain functional structure [@edwards2013; @matuoka2020], and the inclusion of more heavily impacted sites would not necessarily change the result.
